Can we explain the popularity of Netflix Shows?

### 2023-01-21 submission.Rmd
save changes

# Packages
Before we get started. We will load all the relevant Pacakages
```{r load packages, message=FALSE}
library(reticulate)
library(DBI)
library(dplyr)
library(lubridate)
library(tidyr)
library(data.table)
library(quanteda)
library(tm)
library(lsa)
library("quanteda.textmodels")
library(ggplot2)
library(kableExtra)
library(Hmisc)
```

@@

@@

1. Type
``` {r}
view <- df %>% group_by(type) %>% summarise(count = n())
print(view)
```
The type feature looks clean, no action will be taken on it.
Action: None

2. director
``` {r}
view <- df %>% group_by(director) %>% summarise(count = n())
print(view)
```
Some of the rows have more than one director. 
Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable

3. Cast
``` {r}
view <- df %>% group_by(cast) %>% summarise(count = n())
print(view)
```
As expected, many Shows have more than one cast member. 
Action: Similar to what will be done with the Director Feature, I will make mapping tables and use feature engineering to capture this variable

3. Country
``` {r}
view <- df %>% group_by(country) %>% summarise(count = n())
print(view)
```
Some shows originated from several different countries.
Action: Similar to what will be done with the Director and Cast Feature, I will make mapping tables and use feature engineering to capture this variable.

4. Date Added
``` {r}
view <- df %>% group_by(date_added) %>% summarise(count = n())
print(view)
print(typeof(df$date_added))
```
Date Added is in the character format.
Action: Change this to date format
``` {r}
df$date_added <- mdy(df$date_added)
```

5. Release Year
``` {r}
view <- df %>% group_by(release_year) %>% summarise(count = n()) # Show release_year and count by each release_year
print(view)
print(typeof(df$release_year))
```
Release Year has the integer type. No noticable structural error.
Action: None

6. Rating
``` {r}
view <- df %>% group_by(rating) %>% summarise(count = n()) # Show release_year and count by each release_year
print(view)
```
There are several categories which have the same meaning.
Action: Consolidate the categories

Consolidate the categories of the Rating Feature
```{r}
df$rating[df$rating == "PG-13" ] <- "PG"
df$rating[df$rating == "TV-PG" ] <- "PG"
df$rating[df$rating == "TV-14" ] <- "PG"
df$rating[df$rating == "TV-G" ] <- "G"
df$rating[df$rating == "TV-MA" ] <- "R"
df$rating[df$rating == "NC-17" ] <- "R"
df$rating[df$rating == "TV-Y7" ] <- "Y"
df$rating[df$rating == "TV-Y7-FV" ] <- "Y"
df$rating[df$rating == "TV-Y" ] <- "Y"
df$rating[df$rating == "NR" ] <- "UR"
df$rating[df$rating == "66 min" ] <- "UR"
df$rating[df$rating == "84 min" ] <- "UR"

@@

7. Duration
``` {r}
view <- df %>% group_by(duration) %>% summarise(count = n()) # Show duration and count by each release_year
print(view)
```
Durations with two different units are in the same feature. Also, we can remove their units to make it integers.
Action: Split column into two different types of durations, remove units
``` {r}
df$duration[df$duration ==""] <- NA
df$duration_min <- ifelse(grepl("min", df$duration),df$duration,NA)
df$duration_season <- ifelse(grepl("Season", df$duration),df$duration,NA)
print(head(df, 10))
```

Remove string from duration and convert character to integer
``` {r}
df$duration_min <-  gsub('min','',df$duration_min)
df$duration_min <- as.numeric(df$duration_min)
df$duration_season <-  gsub('Seasons','',df$duration_season)
df$duration_season <-  gsub('Season','',df$duration_season)
df$duration_season <- as.numeric(df$duration_season)
print(head(df,10))
```

@@

8. Genre
``` {r}
view <- df %>% group_by(genre) %>% summarise(count = n()) # Show genre and count by each genre
print(view)
```
Some of the rows have more than one genre. 
Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable

9. Plot
Plot contains text data.
Action: Use Latent Semantic Analysis to categorize plots

10. Google Score
``` {r}
view <- df %>% group_by(google_score) %>% summarise(count = n()) # Show google_score and count by each google_score
print(view)
```
Symbol exist and type is character
Action: remove symbol and convert type to numeric

11. Google Score
``` {r}
df$google_score<-gsub("%","",as.character(df$google_score))
df <- transform(df, google_score = as.numeric(google_score))
```

12. Google Language
``` {r}
print(head(df$google_language), 10)
```
Clear that a lot of data is missing.
Action: Extract feature from it (present/absent)

Transform google_language and google_genre feature into present/absent because it was not scrappable
view <- df %>% group_by(google_language) %>% summarise(count = n())  # Show categories and count by each category
df$google_language <- ifelse(df$google_language =="", "absent", "present")
print(view)
df$google_genre <- ifelse(df$google_genre =="", "absent", "present")
view <- df %>% group_by(google_genre) %>% summarise(count = n())
print(view)

13. Google Genre

``` {r}
print(head(df$google_language), 10)
```
Clear that a lot of data is missing.
Action: Extract feature from it (present/absent)

``` {r}
#write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
#df <- read.csv(file = 'datasets/view_main_cleaned.csv')
```

## Handle Missing data

### Missing Data
``` {r}
#desc <- describe(df)
#print(desc)
```

```{r}
#feature <- new_names # retrieving all the column names

#NA_Count <- c(
#  toString(count_blanks('id'))
# , toString(count_blanks('type'))
# , toString(count_blanks('title'))
# , toString(count_blanks('director'))
# , toString(count_blanks('cast'))
# , toString(count_blanks('country'))
# , toString(count_blanks('date_added'))
# , toString(count_blanks('release_year'))
# , toString(count_blanks('rating'))
# , toString(count_blanks('duration'))
# , toString(count_blanks('genre'))
# , toString(count_blanks('plot'))
# , toString(count_blanks('google_score'))
# , toString(count_blanks('google_language'))
# , toString(count_blanks('google_genre'))
# , toString(count_blanks('google_plot')))
#NA_Count <- data.frame(feature, NA_Count)

#print(NA_Count)

* Validate

* Step 3: Filter unwanted outliers

# Cleaning each feature (sub header) 
Look for inconsistencies, duplicates, outliers, etc. 
Changing type and formats
Recatagorize 
+ id - check completeness
+ type - summary 
+ title - check completeness
+ director - summary
+ cast - summary 
+ country - summary
+ date_added - 
+ release_year
+ rating
+ duration
+ genre
+ plot
+ google_score
+ google_language
+ google_genre
+ google_plot

Handle missing data (sub header)
Missing reviews (sub sub header)
Remove rows with no data on reviews
< code >

Analysing missing datapoints (sub sub header)
< code >
Pretty useless to have these features
But I transform the fields into present/absent
Just in case it has predictive capabilities
< code >

# Mapping Tables 
# Build Country Mapping Table
``` {r}

@@

# # Build Director Mapping Table
``` {r}

director_mapping = subset(director_mapping, select = c(id, director))
director_mapping$director <- trimws(director_mapping$director , which = c("left"))
write.csv(director_mapping, "datasets/mapping_director.csv", row.names=FALSE)
```

# # Build Cast Mapping Table
``` {r}
cast_mapping <- df %>%
    mutate(cast = strsplit(as.character(cast), ",")) %>%
    unnest(cast)

# # Build Genre Mapping Table
``` {r}
genre_mapping <- df %>%
    mutate(genre = strsplit(as.character(genre), ",")) %>%
    unnest(genre)

@@

# Trim dataset for better performance
``` {r}
df = subset(df, select = -c(country,director,cast,genre) )
```

#Get top 100 actors and actress from IMDB list

# Feature engineering - categories actors based on how popular they are 
``` {r}
popularActors <- read.csv(file = 'datasets/dataset_popular_actors.csv')

# Create new column and set default value to "top 1000"
popularActors$rank_category <- "top 1000"
setDT(popularActors)

popularActors$rank_category[popularActors$Position < 501 ] <- "top 500"
popularActors$rank_category[popularActors$Position < 201 ] <- "top 200"
popularActors$rank_category[popularActors$Position < 101 ] <- "top 100"
popularActors$rank_category[popularActors$Position < 51 ] <- "top 50"
popularActors$rank_category[popularActors$Position < 21 ] <- "top 20"
popularActors$rank_category[popularActors$Position < 11 ] <- "top 10"

popularActors <- separate(popularActors, Description, c("Points", "Description"))
popularActors <- transform(popularActors, Points = as.numeric(Points))

# View(popularActors)

write.csv(popularActors, "datasets/view_popular_actors.csv", row.names=FALSE)
```

# Feature engineering - categories actors based on how popular they are 
``` {r}
popularActresses <- read.csv(file = 'datasets/dataset_popular_actresses.csv')

# Create new column and set default value to "top 1000"
popularActresses$rank_category <- "top 1000"
setDT(popularActresses)

popularActresses$rank_category[popularActresses$Position < 501 ] <- "top 500"
popularActresses$rank_category[popularActresses$Position < 201 ] <- "top 200"
popularActresses$rank_category[popularActresses$Position < 101 ] <- "top 100"
popularActresses$rank_category[popularActresses$Position < 51 ] <- "top 50"
popularActresses$rank_category[popularActresses$Position < 21 ] <- "top 20"
popularActresses$rank_category[popularActresses$Position < 11 ] <- "top 10"

# Get points from actresses
popularActresses <- separate(popularActresses, Description, c("Points", "Description"))
popularActresses <- transform(popularActresses, Points = as.numeric(Points))

# View(popularActresses)

write.csv(popularActresses, "datasets/view_popular_actresses.csv", row.names=FALSE)
```

# Feature engineering - categories directors based on how popular they are 
``` {r}
popularDirectors <- read.csv(file = 'datasets/dataset_popular_directors.csv')

# Create new column and set default value to "top 1000"
popularDirectors$rank_category <- "top 1000"
setDT(popularDirectors)

popularDirectors$rank_category[popularDirectors$Position < 501 ] <- "top 500"
popularDirectors$rank_category[popularDirectors$Position < 201 ] <- "top 200"
popularDirectors$rank_category[popularDirectors$Position < 101 ] <- "top 100"
popularDirectors$rank_category[popularDirectors$Position < 51 ] <- "top 50"
popularDirectors$rank_category[popularDirectors$Position < 21 ] <- "top 20"
popularDirectors$rank_category[popularDirectors$Position < 11 ] <- "top 10"

#Get points from directors
popularDirectors <- separate(popularDirectors, Description, c("Points", "Description"))
popularDirectors <- transform(popularDirectors, Points = as.numeric(Points))

# View(popularDirectors)

write.csv(popularDirectors, "datasets/view_popular_directors.csv", row.names=FALSE)
```

# Create an ephemeral in-memory RSQLite database
#``` {r}

main <- read.csv(file = 'datasets/view_main_trimmed.csv')
cast <- read.csv(file = 'datasets/mapping_cast.csv')
actorsPoints <- read.csv(file = 'datasets/view_popular_actors.csv')
actressesPoints <- read.csv(file = 'datasets/view_popular_actresses.csv')
directors <- read.csv(file = 'datasets/mapping_director.csv')
directorsPoints <- read.csv(file = 'datasets/view_popular_directors.csv')

dbWriteTable(con, "main", main)
dbWriteTable(con, "cast", cast)
dbWriteTable(con, "actorsPoints", actorsPoints)
dbWriteTable(con, "actressesPoints", actressesPoints)
dbWriteTable(con, "directors", directors)
dbWriteTable(con, "directorsPoints", directorsPoints)

# Attach the points to the mapping table
query <- "SELECT c.id
                ,c.cast
                ,CASE WHEN a.Points IS NOT NULL THEN a.Points
                WHEN b.Points IS NOT NULL THEN b.Points 
                ELSE 0 END AS Points
                FROM cast c
                LEFT JOIN actorsPoints a ON c.cast = a.Name
                LEFT JOIN actressesPoints b ON c.cast = b.Name"
res <- dbSendQuery(con, query)
castPointsMapping <- dbFetch(res)
dbClearResult(res)

dbWriteTable(con, "castPointsMapping", castPointsMapping)

#Attach the director to the mapping table
query <- "SELECT a.id
                ,a.director
                ,CASE WHEN d.Points IS NOT NULL THEN d.Points
                ELSE 0 END AS Points
                FROM directors a
                LEFT JOIN directorsPoints d ON a.director = d.Name"
res <- dbSendQuery(con, query)
directorPointsMapping <- dbFetch(res)
dbClearResult(res)

@@

query <- "SELECT a.*
        , CASE WHEN c.Points IS NOT NULL THEN max(c.Points)
        ELSE 0 END AS cast_points
        , CASE WHEN d.Points IS NOT NULL THEN max(d.Points)
        ELSE 0 END AS director_points
        FROM main a 
        LEFT JOIN castPointsMapping c ON a.id = c.id 
        LEFT JOIN directorPointsMapping d ON a.id = d.id 
        GROUP BY a.id"

@@

dbClearResult(res)
#```

# Seperate google_scores into bins
#``` {r}
# df$google_scoreClass <- cut(df$google_score, breaks=c(0,60,70,80,90,100), labels=c("0-60","61-70","71-80","81-90","90-100"))

write.csv(df, "datasets/view_main_features.csv", row.names=FALSE)

# Latent Semantic Analysis of Plot and google plot data
``` {r}

```
# load data

@@

>>>>

# Packages
Before we get started. We will load all the relevant Pacakages
```{r load packages, message=FALSE}
library(reticulate)
library(DBI)
library(dplyr)
library(lubridate)
library(tidyr)
library(data.table)
library(quanteda)
library(tm)
library(lsa)
library("quanteda.textmodels")
library(ggplot2)
library(kableExtra)
library(Hmisc)
library(ggcorrplot)
```

@@

## Handle Missing data
``` {r}
#desc <- describe(df)
#print(desc)
```

```{r}
feature <- new_names # retrieving all the column names

NA_Count <- c(
 toString(count_blanks('id'))
, toString(count_blanks('type'))
, toString(count_blanks('title'))
, toString(count_blanks('director'))
, toString(count_blanks('cast'))
, toString(count_blanks('country'))
, toString(count_blanks('date_added'))
, toString(count_blanks('release_year'))
, toString(count_blanks('rating'))
, toString(count_blanks('duration'))
, toString(count_blanks('genre'))
, toString(count_blanks('plot'))
, toString(count_blanks('google_score'))
, toString(count_blanks('google_language'))
, toString(count_blanks('google_genre'))
, toString(count_blanks('google_plot')))
NA_Count <- data.frame(feature, NA_Count)

print(NA_Count)

Google Genre and Google Language are missing in a big proportion of rows.
Action: Instead of removing the feature entirely, I'd like to extract some value out of it. I will transform google_language and google_genre feature into present/absent.

``` {r}
df$google_language <- ifelse(df$google_language =="", "absent", "present")
view <- df %>% group_by(google_language) %>% summarise(count = n())
print(view)
```
``` {r}
df$google_genre <- ifelse(df$google_genre =="", "absent", "present")
view <- df %>% group_by(google_genre) %>% summarise(count = n())
print(view)
```

@@

### 1. Type
``` {r}
view <- df %>% group_by(type) %>% summarise(count = n())
print(view)
```
The type feature looks clean, no action will be taken on it.
Action: None

### 2. director
``` {r}
view <- df %>% group_by(director) %>% summarise(count = n())
print(view)
```
Some of the rows have more than one director. 
Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable

### 3. Cast
``` {r}
view <- df %>% group_by(cast) %>% summarise(count = n())
print(view)
```
As expected, many Shows have more than one cast member. 
Action: Similar to what will be done with the Director Feature, I will make mapping tables and use feature engineering to capture this variable

### 4. Country
``` {r}
view <- df %>% group_by(country) %>% summarise(count = n())
print(view)
```
Some shows originated from several different countries.
Action: Similar to what will be done with the Director and Cast Feature, I will make mapping tables and use feature engineering to capture this variable.

### 5. Date Added
``` {r}
view <- df %>% group_by(date_added) %>% summarise(count = n())
print(view)
print(typeof(df$date_added))
```
Date Added is in the character format.
Action: Change this to date format
``` {r}
df$date_added <- mdy(df$date_added)
```

### 6. Release Year
``` {r}
view <- df %>% group_by(release_year) %>% summarise(count = n()) # Show release_year and count by each release_year
print(view)
print(typeof(df$release_year))
```
Release Year has the integer type. No noticable structural error.
Action: None

### 7. Rating
``` {r}
view <- df %>% group_by(rating) %>% summarise(count = n()) # Show release_year and count by each release_year
print(view)
```
There are several categories which have the same meaning.
Action: Consolidate the categories

Consolidate the categories of the Rating Feature
```{r}
df$rating[df$rating == "PG-13" ] <- "PG"
df$rating[df$rating == "TV-PG" ] <- "PG"
df$rating[df$rating == "TV-14" ] <- "PG"
df$rating[df$rating == "TV-G" ] <- "G"
df$rating[df$rating == "TV-MA" ] <- "R"
df$rating[df$rating == "NC-17" ] <- "R"
df$rating[df$rating == "TV-Y7" ] <- "Y"
df$rating[df$rating == "TV-Y7-FV" ] <- "Y"
df$rating[df$rating == "TV-Y" ] <- "Y"
df$rating[df$rating == "NR" ] <- "UR"
df$rating[df$rating == "66 min" ] <- "UR"
df$rating[df$rating == "84 min" ] <- "UR"
df$rating[df$rating == ""] <- "UR"

@@

### 8. Duration
``` {r}
view <- df %>% group_by(duration) %>% summarise(count = n()) # Show duration and count by each release_year
print(view)
```
Durations with two different units are in the same feature. Also, we can remove their units to make it integers.
Action: Split column into two different types of durations, remove units
``` {r}
df$duration[df$duration ==""] <- NA
df$duration_min <- ifelse(grepl("min", df$duration),df$duration,NA)
df$duration_season <- ifelse(grepl("Season", df$duration),df$duration,NA)
print(head(df[,c("title","duration_min","duration_season")]))
```

Remove string from duration and convert character to integer
``` {r}
df$duration_min <-  gsub('min','',df$duration_min)
df$duration_min <- as.numeric(df$duration_min)
df$duration_season <-  gsub('Seasons','',df$duration_season)
df$duration_season <-  gsub('Season','',df$duration_season)
df$duration_season <- as.numeric(df$duration_season)
print(head(df[,c("title","duration_min","duration_season")]))
```

@@

### 9. Genre
``` {r}
view <- df %>% group_by(genre) %>% summarise(count = n()) # Show genre and count by each genre
print(view)
```
Some of the rows have more than one genre. 
Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable

### 10. Plot
Plot contains text data.
Action: Use Latent Semantic Analysis to categorize plots

### 11. Google Score
``` {r}
view <- df %>% group_by(google_score) %>% summarise(count = n()) # Show google_score and count by each google_score
print(view)
```
Symbol exist and type is character
Action: remove symbol and convert type to numeric

``` {r}
df$google_score<-gsub("%","",as.character(df$google_score))
df <- transform(df, google_score = as.numeric(google_score))
```

### 13. Google language
Feature was engineered already, so it is clean.

### 14. Google genre
Feature was engineered already, so it is clean.

### 15. Goolge Plot
Goolge Plot contains text data.
Action: Use Latent Semantic Analysis to categorize plots

# Filter unwanted outliers (pending section)

# Data Transformation

## Mapping Tables 
As talked about in the Data Cleaning Section above, I will build a mapping table for Cast, Director, Country and Genre. 
This would help reflect their one to many relationship.

### Build Director Mapping Table
``` {r}

director_mapping = subset(director_mapping, select = c(id, director))
director_mapping$director <- trimws(director_mapping$director , which = c("left"))

write.csv(director_mapping, "datasets/mapping_director.csv", row.names=FALSE)
```

### Build Cast Mapping Table
``` {r}
cast_mapping <- df %>%
    mutate(cast = strsplit(as.character(cast), ",")) %>%
    unnest(cast)

### Build Country Mapping Table
``` {r}

@@

### Build Genre Mapping Table
``` {r}
genre_mapping <- df %>%
    mutate(genre = strsplit(as.character(genre), ",")) %>%
    unnest(genre)

@@

# Feature engineering  
### Cast
IMDB provides a dataset of Top 1000 Actors and Actresses based on their popularity.

Analyse the IMDB actors dataset
``` {r}
IMDBActors <- read.csv(file = 'datasets/dataset_popular_actors.csv')
print(head(IMDBActors))
```
The dataset  includes a numeric measure of their popularity in the column "Points".
I clean that column so that it can be engineered, transformed and used as a feature in the main dataset.
I write the data into a csv as a view

```{r}
IMDBActors <- separate(IMDBActors, Description, c("Points", "Description"))
IMDBActors <- transform(IMDBActors, Points = as.numeric(Points))
```

I do the same with the IMDB Actress dataset
``` {r}
IMDBActress <- read.csv(file = 'datasets/dataset_popular_actresses.csv')

IMDBActress <- separate(IMDBActress, Description, c("Points", "Description"))
IMDBActress <- transform(IMDBActress, Points = as.numeric(Points))

Once that is done, I attach the points of each Actor/Actress to the cast mapping table. (Not all cast members in the table have points because they may not be in the IMDB list)
``` {r message=FALSE}
con <- dbConnect(RSQLite::SQLite(), ":memory:")

dbWriteTable(con, "cast", cast_mapping)
dbWriteTable(con, "actorsPoints", IMDBActors)
dbWriteTable(con, "actressesPoints", IMDBActress)

query <- "SELECT c.id
                ,c.cast
                ,CASE WHEN a.Points IS NOT NULL THEN a.Points
                WHEN b.Points IS NOT NULL THEN b.Points 
                ELSE 0 END AS Points
                FROM cast c
                LEFT JOIN actorsPoints a ON c.cast = a.Name
                LEFT JOIN actressesPoints b ON c.cast = b.Name"
res <- dbSendQuery(con, query)

castPointsMapping <- dbFetch(res)

dbWriteTable(con, "castPointsMapping", castPointsMapping)
```

For each Show/Movie, take the points of the most famous Actor/Actress and attach it to the main table
```{r}
dbWriteTable(con, "main", df)

query <- "SELECT a.*
        , CASE WHEN c.Points IS NOT NULL THEN max(c.Points)
        ELSE 0 END AS cast_points
        FROM main a 
        LEFT JOIN castPointsMapping c ON a.id = c.id 
        GROUP BY a.id"

print(head(df[,c("title","cast_points")]))

```
### Directors
I do the same for directors
``` {r message=FALSE} 
IMDBDirectors <- read.csv(file = 'datasets/dataset_popular_directors.csv')

IMDBDirectors <- separate(IMDBDirectors, Description, c("Points", "Description"))
IMDBDirectors <- transform(IMDBDirectors, Points = as.numeric(Points))

dbWriteTable(con, "main_2", df)
dbWriteTable(con, "directorsPoints", IMDBDirectors)
dbWriteTable(con, "director", director_mapping)

query <- "SELECT a.id
                ,a.director
                ,CASE WHEN d.Points IS NOT NULL THEN d.Points
                ELSE 0 END AS Points
                FROM director a
                LEFT JOIN directorsPoints d ON a.director = d.Name"
res <- dbSendQuery(con, query)
directorPointsMapping <- dbFetch(res)
dbClearResult(res)

@@

query <- "SELECT a.*
        , CASE WHEN d.Points IS NOT NULL THEN max(d.Points)
        ELSE 0 END AS director_points
        FROM main_2 a 
        LEFT JOIN directorPointsMapping d ON a.id = d.id 
        GROUP BY a.id"

@@

dbClearResult(res)

print(head(df[,c("title","director_points")]))
```

Before carrying out further analysis, I disconnect from SQLite I write the main dataframe into a csv 
``` {r}
dbDisconnect(con)
write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
```

# Feature Engineering -  Latent Semantic Analysis of Plot and google plot data
# load data

@@

# Exploratory Data Analysis

### Corelation between numeric features
Before we get started, it would be useful to know how correlated the features are. I do this for the numeric features. 
``` {r}
numeric_features <-  select_if(df, is.numeric)
corr<- cor(numeric_features)
ggcorrplot(corr)
plot()
```

### Findings
* Release Year and Google Score are slightly negatively correlated
* Director Points and and Google Score are also slightly positively correlated
* Cast Points and and Google Score are also slightly positively correlated 
* Release Year and Director Points are slightly negatively correlated
* Release Year and Cast Points are slightly negatively correlated
